Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-02-15 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
revision of discussion

\section{Discussion}
In this work we investigate the effects of membrane permeability to
water on the membrane hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable inextensible membrane always
inflates to maximize the water content inside the inextensible membrane (a fixed
length (area) in two (three) dimensions.) Results from analysis and
numerical simulations show that such relaxation of a semipermeable
inextensible membrane  is characterized by a rescaled time $\beta t$. We further
illustrate that the relaxation process consists of at least two phases:
The first phase is dominated by the balance between membrane traction
and viscous stress at early times (up to five minutes), when the inextensible membrane
behaves like an impermeable membrane. The second phase sets in after a
few hours, when water influx begins to dominate and inflate the semipermeable membrane.
Over a time scale of more than four weeks, a semipermeable membrane is
fully inflated, independent of its initial surface-to-volume ratio.

>>>>

\section{Discussion}
In this work we investigate the effects of membrane permeability to
water on the membrane hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable inextensible
membrane always inflates to maximize the water content inside the
inextensible membrane (a fixed length (area) in two (three) dimensions).
Results from analysis and numerical simulations show that such
relaxation of a semipermeable inextensible membrane is characterized by
a rescaled time $\beta t$. In linear and non-linear shear flows, we show
that the steady-state shape depends on flow rate, while the permeability
sets the time scale required to reach steady state. We further
illustrate that the hydrodynamics consists of at least two phases. The
first phase is dominated by the balance between membrane traction and
viscous stress at early times (up to five minutes), when the
inextensible membrane behaves like an impermeable membrane. The second
phase sets in after a few hours, when water flux begins to dominate and
the semipermeable membrane either inflates or deflates. Over a time
scale of more than four weeks, independent of the initial
surface-to-volume ratio, a semipermeable membrane is fully inflated
(relaxation flow) or has reached its steady-state configuration (shear
flows).
%, independent of
%its initial surface-to-volume ratio.
